comgen-outline

### 2017-12-13 paper/case3-causals.Rmd
fix causal stims table formatting

@@

\begin{table}[]
\centering
\label{tab:causalMaterials}
\resizebox{\textwidth}{!}{
\begin{tabular}{lll}
                   & Plants                                                                                                                                                                                                  & Animals                                                                                                                                                                                                                               \\
Cover story        & On this planet, there is a plant called feps and your team wants to figure out how to make these plants grow tall. Your team runs experiments trying to make feps grow tall with different fertilizers. & On this planet, there are animals called cheebas and your team of scientists wants to figure out how to make these animals sleepy. Your team runs experiments trying to make cheebas sleepy with different naturally occurring herbs. \\
Evidence statement & Your team gave fertilizer B to 100 different feps. Of those 100 treated, 2 feps grew tall.                                                                                                              & Your team gave herb C to 100 different cheebas. Of those 100 treated, 98 cheebas were made sleepy.                                                                                                                                   
\end{tabular}
}
\caption{Cover stories and evidence statements for the two sets of materials used in Expt. 3a\&b}
\end{table}

>>>>

<!-- delta_p = presence-absence -->
<!-- cp = delta_p / normalization ... subset of relevant cases -->
<!-- caus_supp ~ structure induction problem. -->
<!--   - get to delta_p & cp assuming a different integration fn's -->

<!-- caus_support = "" -->
<!-- caus_strength = "This virus causes the disease." -->

@@

\begin{table}[]
\centering
\label{tab:causalMaterials}
\resizebox{\textwidth}{!}{
\begin{tabular}{|p{3cm}|p{6.5cm}|p{6.5cm}|}
\hline
                   & Plants                                                                                                                                                                                                  & Animals                                                                                                                                                                                                                               \\ \hline
Cover story        & On this planet, there is a plant called feps and your team wants to figure out how to make these plants grow tall. Your team runs experiments trying to make feps grow tall with different fertilizers. & On this planet, there are animals called cheebas and your team of scientists wants to figure out how to make these animals sleepy. Your team runs experiments trying to make cheebas sleepy with different naturally occurring herbs. \\ \hline
Evidence statement & Your team gave fertilizer B to 100 different feps. Of those 100 treated, 2 feps grew tall.                                                                                                              & Your team gave herb C to 100 different cheebas. Of those 100 treated, 98 cheebas were made sleepy.    \\   \hline                                                                                                                            
\end{tabular}
}
\caption{Cover stories and evidence statements for the two sets of materials used in Expt. 3a\&b}
\end{table}
